\section{Conclusion}
\label{sec:conclusion}

In this paper, we have presented a model of factors affecting software security, with empirical tests of the model using two datasets. Our results indicate:
\begin{itemize}
	\item In the OpenHub-NVD data, Usage Risk, as measured by user count, has a comparable correlation with Outcomes to Development Risk, as measured by SLOC, Churn, Contributor Count, and project age. Factors outside the team's direct influence have to be considered when evaluating security performance and mitigations. 
	\item Our data corroborate previous research findings that team size and code churn are correlated with discovered vulnerabilities, and do so while controlling for other factors influencing security Outcomes. Measuring the relative impact of each measurement on its construct, and on the model's performance as a whole, supports refining the measurement framework and the theoretical model as further data are collected and evaluated.
	\item Stepping back from the specifics of the case studies, SEM offers means of assessing the relative importance of the measurements taken for software security assessment.
	\item Usage Risk, Development Risk, Adherence, and Outcomes appear to be a reasonable place to start for organizing studies of the factors behind software security success and failure. 
\end{itemize}

Our data suggest that not only software attributes, but the context of software use must be accounted for to assess the state of software security. Researchers and practitioners should measure both software attributes and software usage context when assessing software development practice adherence. That said, our analysis shows correlation, but not causation. Further work including manipulation of variables must be conducted to assess the causes of software insecurity and security. 

\section{Acknowledgements}

This work was supported through an IBM PhD Fellowship, and the USA National Security Agency (NSA) Science of Security Lablet. Any opinions expressed in this material are those of the author(s) and do not necessarily reflect the views of IBM or the NSA. We would like to thank the North Carolina State University Realsearch group for their helpful comments on the paper. We would like to thank Dr. Chris Parnin for his helpful feedback.